\documentclass[10pt]{article}
\usepackage[a4paper, left=0.4in, right=0.4in, top=0.25in, bottom=0.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage[dvipsnames]{xcolor}
\definecolor{darkgray}{rgb}{0.66, 0.66, 0.66}
\definecolor{charcoal}{rgb}{0.21,0.27,0.31}
\definecolor{headliner}{rgb}{0.1,0.20,0.45}
\usepackage{resume_t1}

\begin{document}

\begin{center}
    {\Huge RUSHIL VENKATESWAR}\\
\end{center}

\vspace{-2ex}

\begin{center}
    \small A-411, LBS Hall of Residence, IIT Kharagpur, West Bengal, India - 721 302 | 
    \faMobile\hspace{0.2ex} \textbf{+91 87893 09659}
\end{center}

\vspace{-2.5ex}

\begin{center}
    \Letter\hspace{0.2ex}\href{mailto:rushilv14@gmail.com}{\small rushilv14@gmail.com} | 
    \faLinkedinSquare\hspace{0.2ex} \href{https://www.linkedin.com/in/rushilv4102/}{\small rushilv4102} | 
    \faGithub\hspace{0.2ex} \href{https://github.com/rv4102/}{\small rv4102} |
    \faCode\hspace{0.2ex} \href{http://cse.iitkgp.ac.in/~rushilv/}{\small rushilv} 
\end{center}

\vspace{-2.5ex}
\roottitle{\Large{\color{headliner} EDUCATION}} 
{\color{headliner} \spacedhrule{0.2ex}{2.0ex}}

\vspace{-1ex}
\renewcommand{\arraystretch}{1.5}
\begin{center}
    \indent \begin{tabular}{ |@{\hskip 0.115in}l @{\hskip 0.115in} |@{\hskip 0.115in}l @{\hskip 0.115in} |@{\hskip 0.115in}l @{\hskip 0.115in} |@{\hskip 0.115in}l @{\hskip 0.115in} |l }
    \hline \textbf{Degree} & \textbf{Institute} & \textbf{Year} & \textbf{CGPA / \%} \\ 
    \hline {Dual Degree} in Computer Science \& Engineering & IIT Kharagpur  & 2020 - 2025 &          \textbf{8.79 / 10}\\
    \hline Indian School Certificate & Little Flower School, Jamshedpur & 2018 - 2020 &  \textbf{96.25\%} \\
    \hline Indian Certificate of Secondary Education & Little Flower School, Jamshedpur & 2007 - 2018 &  \textbf{95.40\% } \\
    \hline
    \end{tabular}
\end{center}
% \\

% \vspace{-2.5ex}
% \roottitle{\Large{\color{headliner} INDUSTRIAL EXPERIENCE}}
% {\color{headliner} \spacedhrule{0.15ex}{1.0ex}}
% %\large {\textbf{Data Science Intern} | CreditMantri} \normalsize
% %\href{https://www.linkedin.com/in/rhea2801/detail/treasury/position:1668636325/?entityUrn=urn\%3Ali\%3Afs%d_profileTreasuryMedia\%3A(ACoAACzQ7ckBrH6LjD1F4-1vqdofvjOQYYXgRVs\%2C1611419363710)&section=position\%3A%1668636325&treasuryCount=1} {\hspace{0.5ex}\faMousePointer}
% %{\hfill} \textbf{Jan - Mar'21}\\[-1.5em]
% %\begin{itemize}\\[1em]
% %\item \textbf{Skills used:} Python, Scikit, Matplotlib, Seaborn\\[-1.75em]
% %\item Worked on a \textbf{regressive income prediction model}, to assist banks %in giving loans to first-time applicants.\\[-1.75em]
% %\item Achieved a \textbf{46\% accuracy within 30\% of actual income level}.

% %\end{itemize}


% %\vspace{-5.0ex}
% %\roottitle{\normalsize{\color{white} INDUSTRIAL EXPERIENCE}}\\[-1em]
% %{\color{white} \spacedhrule{0.15ex}{1.0ex}}
% \large {\textbf{Software Development Intern} | upUgo Sports \& Fitness} \normalsize
% \href{https://github.com/rhea2801/upUgo/blob/main/upUgo_LOR.pdf} {\hspace{0.5ex}\faMousePointer}
% {\hfill} \textbf{Sep - Nov'20}\\[-1.5em]
% \begin{itemize}\\[1em]
% \item \textbf{Skills used:} Javascript,  Python, PHP, MySQL, Bootstrap Studio\\[-1.75em]
% \item Worked to build upUgo's \textbf{TrAIner}, a virtual fitness trainer that uses AI, particularly Computer Vision based algorithms to correct users' movements during an exercise.\\[-1.75em]
% \item Used \textbf{Python's OpenCV} and \textbf{Javascript's ml5.js} libraries primarily to help build the model framework.\\[-1.75em]
% \item Designed the complete \textbf{backend and database architecture}, including individual scoring systems for each exercise, to have the model be seamlessly incorporated on the website\\[-2em]
% \end{itemize}




%The current methods for large data transfer in files or streams were computationally expensive on the host side and slow. Moreover, the data transfer in some products was taking place in a serialised manner, leading to low throughput, especially on the high latency replication links.\\
%My task was to \textbf{build from scratch} a \textbf{High-Throughput Pipeline-able Data Streaming Library} with a minimal overhead above the TCP to support smooth and fast data flow between two hosts. This library provided support to both \textbf{rewindable and non-rewindable} producer and consumers on a \textbf{secured duplex channel}.

\iffalse

\fi

\vspace{-0.1ex}
\roottitle{\Large{\color{headliner} RESEARCH EXPERIENCE}}
{\color{headliner} \spacedhrule{0.15ex}{1.0ex}}
\large {\textbf{Semantic Segmentation of Remote Sensing Images \normalsize{\textit{(Dr. Debasish Chakraborty, ISRO)}}}} \normalsize {\href{https://github.com/rv4102/qnet.git}{\faGithub}}
{\hfill} \textbf{Apr '22 - ongoing}\\[-1.75em]
\begin{itemize}
    \item Studied existing literature on CNNs, deep learning and their usage in the remote sensing context. \\[-1.9em]
    \item Using the Tensorflow framework, built a U-Net like model with improved performance and a fraction of the number of parameters as the original U-Net. \\[-1.9em]
    \item Created various other scripts to perform inference on variable sized images. Tested on Indian context images taken from Google Earth.\\[-1.5em]
\end{itemize}
\large {\textbf{Development of a Python Tutor \normalsize{\textit{(Prof. P. P. Das, IIT Kharagpur)}}}} \normalsize
{\hfill} \textbf{May '22 - July '22}\\[-1.75em]
\begin{itemize}
    \item Used Protégé for making an ontology for Python language. Explored OWLReady python package to create ontologies.\\[-1.9em]
    \item Implemented Frequent Itemset Mining and used it to perform query expansion. \\[-1.5em]
\end{itemize}
\vspace{-2ex}



\roottitle{\Large{\color{headliner} PROJECTS}}
{\color{headliner} \spacedhrule{0.15ex}{1.0ex}}

\large {\textbf{Instance Segmentation and Detection}, \emph{(Software Engineering Lab)} {\href{https://github.com/rv4102/CS29202-Codes/tree/main/A4}{\faGithub}}} \normalsize 
{\hfill} \textbf{Spring '22}\\[-1.75em]
\begin{itemize}
    \item Developed a \textbf{Tkinter based GUI} to display bounding boxes or segmentation masks for the image selected.\\[-1.9em]
    \item Used a pre-trained MaskRCNN model from Pytorch library to generate \textbf{masks} and \textbf{bounding boxes} for a given image and used \textbf{matplotlib} to plot them. \\[-1.9em]
    \item Created a \textbf{python package} from source code. \\[-1.5em]
\end{itemize}
\large {\textbf{KGP-miniRISC Processor}, \emph{(Computer Organisation Lab)} {\href{https://github.com/rv4102/CompOrg-Lab/tree/main/A6_KGP_miniRISC_Processor}{\faGithub}}} \normalsize 
{\hfill} \textbf{Autumn '22}\\[-1.75em]
\begin{itemize}
    \item Developed a 32-bit word length \textbf{single-cycle} instruction execution unit. Hence there is no state and the design is purely combinational. \\[-1.9em]
    \item Successfully dumped the bitstream onto a \textbf{Nexys A7 FPGA board} using Xilinx ISE and ran programs (written in assembly) such as sorting and linear search. \\[-1.9em]
    \item Clock frequency determined by the single longest instruction in the given ISA. \\[-1.5em]
\end{itemize}
\large {\textbf{Students' Auditorium Management Software}, \emph{(Software Engineering Lab)} {\href{https://github.com/rv4102/AudiBooking}{\faGithub}}} \normalsize
{\hfill} \textbf{Spring '22}\\[-1.75em]
\begin{itemize}
    \item An \textbf{auditorium management website} which runs on Localhost (127.0.0.1) and allows the user to maintain a database of shows to be screened along with providing functionality for seat booking.\\[-1.9em]
    \item \textbf{OTP-based login} for users of the software is supported. \\[-1.9em]
    \item Implemented a website using \textbf{Python Flask} for back-end and \textbf{bootstrap} for front-end. \\[-1.5em]
\end{itemize}

\vspace{-2.2ex}
\roottitle{\Large{\color{headliner} AWARDS \& ACHIEVEMENTS}}
{\color{headliner} \spacedhrule{0.15ex}{1.0ex}}
\begin{itemize}[leftmargin=*]
    \item Secured an \textbf{All India Rank} of \textbf{473} in JEE Advanced 2020 (out of 1,60,000 candidates). \\[-2em]
    
    \item Secured an \textbf{All India Rank} of \textbf{1176} in JEE Mains 2020 (out of 1.12 million candidates). \\[-2em]
    
    \item Qualified for KVPY Round 2 in SA Stream in 2019. \\[-2em]

    \item Selected out of 3000 IITians for attending \textbf{Optiver Winter School} conducted by IIT Delhi. \\[-2em]
    
    \item \textbf{1st Position} in \textbf{National Science Day Quiz}, conducted by Gymkhana, IIT Kharagpur. \\[-2em]
    
    \item \textbf{2nd Position} in \textbf{Science of Paper Folding}, conducted by Space Technology Students' Society,  IIT Kharagpur. \\[-2em]
    
    \item Secured \textbf{498 Rank} out of more than 5000 teams in \textbf{ACM ICPC Preliminary Online Round}. \\[-1.8em]
\end{itemize}

\vspace{-1ex}
\roottitle{\Large{\color{headliner} COURSEWORK INFORMATION} }
{\color{headliner} \spacedhrule{0.15ex}{1.0ex}}
\begin{indentsection}
	\skill{University Credit Courses}{Algorithms, Programming and Data Structures, Software Engineering, Systems Programming Lab, Discrete Structures, Statistical Inference, Probability \& Statistics, Linear Algebra, Compilers, Computer Architecture}
	\skill{MOOCs}{Machine Learning \textbf{(Andrew Ng)}, Deep Learning Specialization \textbf{(DeepLearning.AI)}}
\end{indentsection}


\vspace{-1.5ex}
\roottitle{\Large{\color{headliner} SKILLS \& EXPERTISE}}
{\color{headliner} \spacedhrule{0.15ex}{1.0ex}}
\begingroup
    \fontsize{10pt}{12pt}\selectfont
    \vspace{-0.7ex}
	\skill{Languages/ OS }{C,\hspace{0.75ex} C++,\hspace{0.75ex} Python,\hspace{0.75ex} Java, \hspace{0.75ex} LaTeX, \hspace{0.75ex} MATLAB, \hspace{0.75ex} MIPS, \hspace{0.75ex} Verilog, \hspace{0.75ex} macOS}
	\vspace{-0.7ex}
	\skill{Tools }{Git,\hspace{0.75ex} Jupyter Noteboook,\hspace{0.75ex} Google Colaboratory,\hspace{0.75ex} VSCode,\hspace{0.75ex} Shell scripting}
	\vspace{-0.7ex}
    \skill{Libraries \& Frameworks }{C++ STL,\hspace{0.75ex} NumPy,\hspace{0.75ex} Pandas,\hspace{0.75ex} Matplotlib,\hspace{0.75ex} Scikit,\hspace{0.75ex} OpenCV}
\endgroup

\vspace{-0.1ex}
\roottitle{\Large{\color{headliner} POSITIONS of RESPONSIBILITY}}
{\color{headliner} \spacedhrule{0.15ex}{2.0ex}}
\vspace{-1ex}
\large { \textbf{Associate Member} at Business Club, IIT Kharagpur} \normalsize
{\hfill} \textbf{Dec '20 - Sep '21}\\[-1.8em]
\begin{itemize}
    \item Authored a \textbf{Whitepaper on XGBoost} {\href{https://drive.google.com/file/d/1e6BMMkBewwBbj1vg58pLpTyw0jNMvRba/view?usp=sharing}{\faDropbox}}. \\[-2em]
    \item Conducted a webinar on Cryptocurrency with Dr. Akshat Shrivastava as the guest lecturer. \\[-2em]
    \item Participated in an intra-club case study competition and guided newly inducted teammates.\\[-2em]
\end{itemize}

\end{document}
